---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
 knitr::opts_chunk$set(
   collapse = TRUE,
   comment = "#>",
   fig.path = "man/figures/README-",
   out.width = "100%",
   eval = FALSE
 )
```

# agesofman <img src=`r file.path("man", "figures", "logo.png")` align="right" height="139" alt="logo"/>

<!-- badges: start -->
[![CRAN status](https://www.r-pkg.org/badges/version/agesofman)](https://CRAN.R-project.org/package=agesofman)
[![R-CMD-check](https://github.com/agesofman/agesofman/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/agesofman/agesofman/actions/workflows/R-CMD-check.yaml)
[![codecov](https://codecov.io/gh/agesofman/agesofman/branch/main/graph/badge.svg)](https://codecov.io/gh/agesofman/agesofman)
<!-- badges: end -->

## Introduction

The *Ages of Man* project applies advanced statistical methodology on remote sensing agriculture. It is composed of several R packages, as well as other elements, each one focusing on a different application.

  -   `cronus` is an R package that focuses on database creation. It can be used to download and process agricultural, environmental and satellite data from various sources.
  -   `persephone` is an R package that deals with applications in crop development.
  -   `hermes` is an R project that stores files. It includes executable R scripts, shiny applications, rmd reports, plots and more.
  -   `Demeter` is the database created by `cronus` and used by the *Ages of Man* project core team members in their research studies.
  -   `Athena` is a Mendeley collection of research papers available to the *Ages of Man* project team members.

## Installation

You can install the development version of `agesofman` from github by running the following line of code: 

```{r, eval = FALSE}
 devtools::install_github("agesofman/agesofman")
```

## Documentation

Detailed documentation, along with reproducible examples, can be found in the package vignette `vignette(topic = "agesofman", package = "agesofman")`.

## Team

The *Ages of Man* project is developed in the 
[Mathematics Department](https://en.math.uoa.gr/ "Mathematics Department Homepage") of the [University of Athens](https://en.uoa.gr/ "University of Athens Homepage"). The project maintainer is [Ioannis Oikonomidis](http://users.uoa.gr/~goikon/ "Ioannis Oikonomidis Homepage"), working under the supervision of Prof. Samis Trevezas.
